Geometric models reveal behavioral and neural signatures of transforming experiences into memories

### 2020-10-22 paper/main.tex
disable figure placement markers
fixed phrasing of reporting margially significant correlation

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage[sort&compress, numbers, super]{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{placeins}
\usepackage[nofiglist, fighead]{endfloat}
\renewcommand{\includegraphics}[2][]{}

@@

In addition to examining how precisely and distinctively participants recalled individual events, one may also use these metrics to summarize each participant's performance by averaging across a participant's event-wise precision or distinctiveness scores.  This enables us to quantify how precisely a participant tended to recall subtle within-event details, as well as how specific (distinctive) those details were to individual events from the episode.  Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90,~p < 0.001,~95\%~\mathrm{CI} = [0.66, 0.96]$).  This indicates that participants who tended to precisely recount low-level details of episode events also tended to do so in an event-specific way (e.g., as opposed to detailing recurring themes that were present in most or all episode events; this behavior would have resulted in high precision but low distinctiveness).  We found that, across participants, higher precision scores were positively correlated with the numbers of both hand-annotated scenes ($r(15) = 0.60,~p = 0.010,~95\%~\mathrm{CI} = [0.02, 0.83]$) and model-estimated events ($r(15) = 0.90,~p < 0.001,~95\%~\mathrm{CI} = [0.54, 0.96]$) that participants recalled.  Participants' average distinctiveness scores were also marginally correlated with both the hand-annotated ($r(15) = 0.45,~p = 0.068,~95\%~\mathrm{CI} = [-0.21, 0.79]$) and model-estimated ($r(15) = 0.71,~p = 0.001,~95\%~\mathrm{CI} = [-0.07, 0.90]$) numbers of recalled events.

>>>>

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage[sort&compress, numbers, super]{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{placeins}
\usepackage[nofiglist, nomarkers, fighead]{endfloat}
\renewcommand{\includegraphics}[2][]{}

@@

In addition to examining how precisely and distinctively participants recalled individual events, one may also use these metrics to summarize each participant's performance by averaging across a participant's event-wise precision or distinctiveness scores.  This enables us to quantify how precisely a participant tended to recall subtle within-event details, as well as how specific (distinctive) those details were to individual events from the episode.  Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90,~p < 0.001,~95\%~\mathrm{CI} = [0.66, 0.96]$).  This indicates that participants who tended to precisely recount low-level details of episode events also tended to do so in an event-specific way (e.g., as opposed to detailing recurring themes that were present in most or all episode events; this behavior would have resulted in high precision but low distinctiveness).  We found that, across participants, higher precision scores were positively correlated with the numbers of both model-estimated events ($r(15) = 0.90,~p < 0.001,~95\%~\mathrm{CI} = [0.54, 0.96]$) and hand-annotated scenes ($r(15) = 0.60,~p = 0.010,~95\%~\mathrm{CI} = [0.02, 0.83]$) that participants recalled.  Participants' average distinctiveness scores were also correlated with their numbers of model-estimated recalled events ($r(15) = 0.71,~p = 0.001,~95\%~\mathrm{CI} = [-0.07, 0.90]$) and marginally significantly correlated with their numbers of hand-annotated ($r(15) = 0.45,~p = 0.068,~95\%~\mathrm{CI} = [-0.21, 0.79]$).
